---
title: "DSO599 Final Project"
author: "Rachel Sung"
date: "9/26/2020"
output: html_document
---

### Install required packages
```{r}
#install.packages("ggplot2")
library("ggplot2")
#install.packages("sentimentr")
library('sentimentr')
#install.packages('syuzhet')
library('syuzhet')
#install.packages("tm")
library("tm")
#install.packages("NLP")
library("NLP")
#install.packages("wordcloud")
library("wordcloud")
#install.packages("RColorBrewer")
library("RColorBrewer")
library("readxl")
#install.packages("dplyr")
library("dplyr")
```

### Import data
```{r}
data = read_excel("/Users/rachel/Downloads/MIA vs BOS - Game 5 - Combined Data V3.xlsx")
View(data)
```

### Seperate data by Category
```{r}
data_heat = data %>%
  filter(Category == "Heat")

data_celtics = data %>%
  filter(Category == "Celtics")

data_mixed = data %>%
  filter(Category == "Mixed")
```

### Emotion Vectors
```{r}
boston_nrc_sentiment <- get_nrc_sentiment(data_celtics$tweet)
miami_nrc_sentiment <- get_nrc_sentiment(data_heat$tweet)
mixed_nrc_sentiment <- get_nrc_sentiment(data_mixed$tweet)
```

### Visualize
```{r}
#install.packages("RColorBrewer")
library("RColorBrewer")
```

```{r}
barplot(sort(colSums(prop.table(boston_nrc_sentiment[, 1:8]))),
          horiz = TRUE,
          cex.names = 0.7, 
          las = 1, 
          main = "Emotions in Boston Celtics Tweets", xlab="Percentage",
          col = c("#E69F00", "#E69F00","#009E73","#E69F00","#E69F00","#009E73","#009E73","#009E73"))
```
```{r}
barplot(
  sort(colSums(prop.table(miami_nrc_sentiment[, 1:8]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in Miami Heat Tweets", xlab="Percentage",
  col = c("red", "#E69F00","#E69F00","red","red","#E69F00","#E69F00","red")
)
```
```{r}
barplot(
  sort(colSums(prop.table(mixed_nrc_sentiment[, 1:8]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in Mixed Tweets", xlab="Percentage",
  col = c("blue", "blue","#E69F00","#E69F00","#E69F00","blue","#E69F00","blue")
)
```

### Subtracting Emotions
```{r}
barplot(
  sort(colSums(prop.table(boston_nrc_sentiment[, 1:8])) - colSums(prop.table(miami_nrc_sentiment[, 1:8]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Boston Emotions - Miami Emotions", xlab="Percentage",
  col = c("#E69F00", "#E69F00","#E69F00","#E69F00","blue","blue","blue","blue")
)
```

### Positive-Negative Emotions
```{r}
barplot(
  sort(colSums(prop.table(boston_nrc_sentiment[, 9:10]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Pos-Neg Emotions: Boston", xlab="Percentage",
  col = c("#E69F00","green")
)
```
```{r}
barplot(
  sort(colSums(prop.table(miami_nrc_sentiment[, 9:10]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Pos-Neg Emotions: Miami", xlab="Percentage",
  col = c("#E69F00","red")
)
```
```{r}
barplot(
  sort(colSums(prop.table(mixed_nrc_sentiment[, 9:10]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Pos-Neg Emotions: Mixed", xlab="Percentage",
  col = c("blue","#E69F00")
)
```

### Function for plotting wordcloud
```{r}
f_plot_wordcloud <- function (tweet_texts, nrc_sentiment) {
  
  all = c(
    paste(tweet_texts[nrc_sentiment$anger > 0], collapse=" "),
    paste(tweet_texts[nrc_sentiment$anticipation > 0], collapse=" "),
    paste(tweet_texts[nrc_sentiment$disgust > 0], collapse=" "),
    paste(tweet_texts[nrc_sentiment$fear > 0], collapse=" "),
    paste(tweet_texts[nrc_sentiment$joy > 0], collapse=" "),
    paste(tweet_texts[nrc_sentiment$sadness > 0], collapse=" "),
    paste(tweet_texts[nrc_sentiment$surprise > 0], collapse=" "),
    paste(tweet_texts[nrc_sentiment$trust > 0], collapse=" ")
  )
  all <- removeWords(all, stopwords("english"))
  # create corpus
  corpus <- Corpus(VectorSource(all))
  #
  # create term-document matrix
  tdm <- TermDocumentMatrix(corpus)
  #
  # convert as matrix
  tdm <- as.matrix(tdm)
  tdm1 <- tdm[nchar(rownames(tdm)) < 15,]
  #
  # add column names
  colnames(tdm) = c('anger', 'anticipation', 'disgust', 'fear', 'joy', 'sadness', 'surprise', 'trust')
  colnames(tdm1) <- colnames(tdm)
  comparison.cloud(tdm1, random.order=FALSE,
                   colors = c("#00B2FF", "red", "#FF0099", "#6600CC", "green", "orange", "blue", "brown"), title.size=1.8, max.words=300, scale=c(2,.8),rot.per=0.4)
}
```

### Wordcloud
```{r}
## Boston
f_plot_wordcloud(data_celtics$tweet,boston_nrc_sentiment)
```
```{r}
# Miami
f_plot_wordcloud(data_heat$tweet,miami_nrc_sentiment)
```
```{r}
# Mixed
f_plot_wordcloud(data_mixed$tweet,mixed_nrc_sentiment)
```

### Seperate data by Time Frame
```{r}
data_before = data %>%
  filter(data$`Time Frame` == "Before Game")

data_half = data %>%
  filter(data$`Time Frame` == "Halftime")

data_post = data %>%
  filter(data$`Time Frame` == "Post Game")

data_Q1 = data %>%
  filter(data$`Time Frame` == "Q1")

data_Q2 = data %>%
  filter(data$`Time Frame` == "Q2")

data_Q3 = data %>%
  filter(data$`Time Frame` == "Q3")

data_Q4 = data %>%
  filter(data$`Time Frame` == "Q4")
```

### Emotion Vector
```{r}
before_nrc_sentiment <- get_nrc_sentiment(data_before$tweet)
half_nrc_sentiment <- get_nrc_sentiment(data_half$tweet)
post_nrc_sentiment <- get_nrc_sentiment(data_post$tweet)
Q1_nrc_sentiment <- get_nrc_sentiment(data_Q1$tweet)
Q2_nrc_sentiment <- get_nrc_sentiment(data_Q2$tweet)
Q3_nrc_sentiment <- get_nrc_sentiment(data_Q3$tweet)
Q4_nrc_sentiment <- get_nrc_sentiment(data_Q4$tweet)
```

### Visualize
```{r}
barplot(
  sort(colSums(prop.table(before_nrc_sentiment[, 1:8]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in Tweets Before Game", xlab="Percentage",
  col = c("#E69F00","#E69F00","#E69F00","#E69F00","blue","blue","blue","blue")
)
```
```{r}
barplot(
  sort(colSums(prop.table(half_nrc_sentiment[, 1:8]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in Tweets Half Game", xlab="Percentage",
  col = c("#E69F00","blue","#E69F00","#E69F00","blue","#E69F00","blue","blue")
)
```
```{r}
barplot(
  sort(colSums(prop.table(post_nrc_sentiment[, 1:8]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in Tweets Post Game", xlab="Percentage",
  col = c("#E69F00","blue","#E69F00","blue","#E69F00","#E69F00","blue","blue")
) 
```
```{r}
barplot(
  sort(colSums(prop.table(Q1_nrc_sentiment[, 1:8]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in Tweets Q1", xlab="Percentage",
  col = c("#E69F00","#E69F00","blue","#E69F00","#E69F00","blue","blue","blue")
)
```
```{r}
barplot(
  sort(colSums(prop.table(Q2_nrc_sentiment[, 1:8]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in Tweets Q2", xlab="Percentage",
  col = c("blue","blue","#E69F00","blue","#E69F00","#E69F00","blue","#E69F00")
)
```
```{r}
barplot(
  sort(colSums(prop.table(Q3_nrc_sentiment[, 1:8]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in Tweets Q3", xlab="Percentage",
  col = c("blue","#E69F00","#E69F00","blue","#E69F00","#E69F00","blue","blue")
)
```
```{r}
barplot(
  sort(colSums(prop.table(Q4_nrc_sentiment[, 1:8]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in Tweets Q4", xlab="Percentage",
  col = c("blue","blue","#E69F00","blue","blue","#E69F00","#E69F00","#E69F00")
)
```

### Wordcloud
```{r}
f_plot_wordcloud(data_before$tweet,before_nrc_sentiment)
f_plot_wordcloud(data_half$tweet,half_nrc_sentiment)
f_plot_wordcloud(data_post$tweet,post_nrc_sentiment)
f_plot_wordcloud(data_Q1$tweet,Q1_nrc_sentiment)
f_plot_wordcloud(data_Q2$tweet,Q2_nrc_sentiment)
f_plot_wordcloud(data_Q3$tweet,Q3_nrc_sentiment)
f_plot_wordcloud(data_Q4$tweet,Q4_nrc_sentiment)
```

### If Timeout/Non-timeout will influence emotions in tweets
```{r}
data_non_timeout = data %>%
  filter(data$`Timeout/Instant Replay` == "Non-Timeout")

data_timeout = data %>%
  filter(data$`Timeout/Instant Replay` == "Timeout")

data_replay = data %>%
  filter(data$`Timeout/Instant Replay` == "Instant Replay/Timeout")

non_timeout_nrc_sentiment <- get_nrc_sentiment(data_non_timeout$tweet)
timeout_nrc_sentiment <- get_nrc_sentiment(data_timeout$tweet)
replay_nrc_sentiment <- get_nrc_sentiment(data_replay$tweet)

```

```{r}
par(mfrow = c(3, 1))
barplot(
  sort(colSums(prop.table(non_timeout_nrc_sentiment[, 9:10]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in Tweets Non-Timeout", xlab="Percentage",
  col = c("#E69F00","blue")
)

barplot(
  sort(colSums(prop.table(timeout_nrc_sentiment[, 9:10]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in Tweets Timeout", xlab="Percentage",
  col = c("#E69F00","blue")
)

barplot(
  sort(colSums(prop.table(replay_nrc_sentiment[, 9:10]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in Tweets Instant Replay", xlab="Percentage",
  col = c("blue","#E69F00")
)
```



### If referee during game will influence emotions in tweets
```{r}
data_ref_yes = data %>%
  filter(data$`Ref Comment` == "Yes")

data_ref_no = data %>%
  filter(data$`Ref Comment` == "No")


ref_yes_nrc_sentiment <- get_nrc_sentiment(data_ref_yes$tweet)
ref_no_nrc_sentiment <- get_nrc_sentiment(data_ref_no$tweet)

```

```{r}
par(mfrow = c(2, 1))
barplot(
  sort(colSums(prop.table(ref_yes_nrc_sentiment[, 9:10]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in Tweets Referee Happens", xlab="Percentage",
  col = c("blue","#E69F00")
)

barplot(
  sort(colSums(prop.table(ref_no_nrc_sentiment[, 9:10]))), 
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Emotions in Tweets No Referee", xlab="Percentage",
  col = c("#E69F00","blue")
)
```



### Understand characters of fans of each team:
```{r}
# Boston
boston_pre = data_celtics%>%
  filter(data_celtics$`Time Frame` == "Before Game")

boston_Q1 = data_celtics%>%
  filter(data_celtics$`Time Frame` == "Q1")

boston_Q2 = data_celtics%>%
  filter(data_celtics$`Time Frame` == "Q2")

boston_half = data_celtics%>%
  filter(data_celtics$`Time Frame` == "Halftime")

boston_Q3 = data_celtics%>%
  filter(data_celtics$`Time Frame` == "Q3")

boston_Q4 = data_celtics%>%
  filter(data_celtics$`Time Frame` == "Q4")

boston_post = data_celtics%>%
  filter(data_celtics$`Time Frame` == "Post Game")
```

```{r}
b_before_nrc_sentiment <- get_nrc_sentiment(boston_pre$tweet)
b_half_nrc_sentiment <- get_nrc_sentiment(boston_half$tweet)
b_post_nrc_sentiment <- get_nrc_sentiment(boston_post$tweet)
b_Q1_nrc_sentiment <- get_nrc_sentiment(boston_Q1$tweet)
b_Q2_nrc_sentiment <- get_nrc_sentiment(boston_Q2$tweet)
b_Q3_nrc_sentiment <- get_nrc_sentiment(boston_Q3$tweet)
b_Q4_nrc_sentiment <- get_nrc_sentiment(boston_Q4$tweet)
```


```{r}
par(mfrow = c(2, 4))
p1 = barplot(
  sort(colSums(prop.table(b_before_nrc_sentiment[, 9:10]))), 
  horiz = FALSE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Before game", xlab="Percentage",
  col = c("#E69F00","blue")
)

p2 = barplot(
  sort(colSums(prop.table(b_Q1_nrc_sentiment[, 9:10]))), 
  horiz = FALSE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Q1", xlab="Percentage",
  col = c("#E69F00","blue")
)

p3 = barplot(
  sort(colSums(prop.table(b_Q2_nrc_sentiment[, 9:10]))), 
  horiz = FALSE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Q2", xlab="Percentage",
  col = c("#E69F00","blue")
)

p4 = barplot(
  sort(colSums(prop.table(b_half_nrc_sentiment[, 9:10]))), 
  horiz = FALSE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Halftime", xlab="Percentage",
  col = c("#E69F00","blue")
)

p5 = barplot(
  sort(colSums(prop.table(b_Q3_nrc_sentiment[, 9:10]))), 
  horiz = FALSE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Q3", xlab="Percentage",
  col = c("#E69F00","blue")
)

p6 = barplot(
  sort(colSums(prop.table(b_Q4_nrc_sentiment[, 9:10]))), 
  horiz = FALSE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Q4", xlab="Percentage",
  col = c("#E69F00","blue")
)

p7 = barplot(
  sort(colSums(prop.table(b_post_nrc_sentiment[, 9:10]))), 
  horiz = FALSE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Post Game", xlab="Percentage",
  col = c("#E69F00","blue")
)

```

```{r}
# Heat
heat_pre = data_heat%>%
  filter(data_heat$`Time Frame` == "Before Game")

heat_Q1 = data_heat%>%
  filter(data_heat$`Time Frame` == "Q1")

heat_Q2 = data_heat%>%
  filter(data_heat$`Time Frame` == "Q2")

heat_half = data_heat%>%
  filter(data_heat$`Time Frame` == "Halftime")

heat_Q3 = data_heat%>%
  filter(data_heat$`Time Frame` == "Q3")

heat_Q4 = data_heat%>%
  filter(data_heat$`Time Frame` == "Q4")

heat_post = data_heat%>%
  filter(data_heat$`Time Frame` == "Post Game")
```

```{r}
h_before_nrc_sentiment <- get_nrc_sentiment(heat_pre$tweet)
h_half_nrc_sentiment <- get_nrc_sentiment(heat_half$tweet)
h_post_nrc_sentiment <- get_nrc_sentiment(heat_post$tweet)
h_Q1_nrc_sentiment <- get_nrc_sentiment(heat_Q1$tweet)
h_Q2_nrc_sentiment <- get_nrc_sentiment(heat_Q2$tweet)
h_Q3_nrc_sentiment <- get_nrc_sentiment(heat_Q3$tweet)
h_Q4_nrc_sentiment <- get_nrc_sentiment(heat_Q4$tweet)
```

```{r}
par(mfrow = c(2, 4))
p1 = barplot(
  sort(colSums(prop.table(h_before_nrc_sentiment[, 9:10]))), 
  horiz = FALSE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Before game", xlab="Percentage",
  col = c("#E69F00","blue")
)

p2 = barplot(
  sort(colSums(prop.table(h_Q1_nrc_sentiment[, 9:10]))), 
  horiz = FALSE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Q1", xlab="Percentage",
  col = c("#E69F00","blue")
)

p3 = barplot(
  sort(colSums(prop.table(h_Q2_nrc_sentiment[, 9:10]))), 
  horiz = FALSE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Q2", xlab="Percentage",
  col = c("#E69F00","blue")
)

p4 = barplot(
  sort(colSums(prop.table(h_half_nrc_sentiment[, 9:10]))), 
  horiz = FALSE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Halftime", xlab="Percentage",
  col = c("#E69F00","blue")
)

p5 = barplot(
  sort(colSums(prop.table(h_Q3_nrc_sentiment[, 9:10]))), 
  horiz = FALSE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Q3", xlab="Percentage",
  col = c("blue","#E69F00")
)

p6 = barplot(
  sort(colSums(prop.table(h_Q4_nrc_sentiment[, 9:10]))), 
  horiz = FALSE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Q4", xlab="Percentage",
  col = c("blue","#E69F00")
)

p7 = barplot(
  sort(colSums(prop.table(h_post_nrc_sentiment[, 9:10]))), 
  horiz = FALSE, 
  cex.names = 0.7, 
  las = 1, 
  main = "Post Game", xlab="Percentage",
  col = c("#E69F00","blue")
)
```



### Correlation
```{r}
# Import combined data with senntiment analysis
new = read_excel("/Users/rachel/Desktop/MIA vs BOS - Game 5 - Combined Data V3_SentimentAnalysis.xlsx")
View(new)

Score_diff = abs(new$`MIA Score Differential`)
new = cbind(new,Score_diff)
data1 = new %>%
  filter(new$`Time Frame` == "Q1" | new$`Time Frame` == "Q2" | new$`Time Frame` == "Q3" | new$`Time Frame` == "Q4" )

cor(data1$retweet_count,data1$negative)
cor(data1$retweet_count,data1$positive)
```

```{r}
cor(data1$`Score_diff`,data1$positive)
cor(data1$`Score_diff`,data1$negative)
```

```{r}
# Boston Score Difference vs Sentiment
boston = new %>%
  filter(Category == "Celtics")

cor(boston$`BOS Score Differential`,boston$positive)
cor(boston$`BOS Score Differential`,boston$negative)
```

```{r}
# Miami Score Difference vs Sentiment
heat = new %>%
  filter(Category == "Heat")

cor(heat$`MIA Score Differential`,heat$positive)
cor(heat$`MIA Score Differential`,heat$negative)
```

